\documentclass[12pt]{article}
\input{../common.tex}

\title{\textbf{Gorkitale: The Truth}}
\author{ByCh4n Group}
\date{\today}

\begin{document}

\maketitle

\section*{Fore-word prologue}

\begin{center}
    \textit{"Let the heavens bear witness that even if the truth is buried seven layers deep within the earth, we shall find it and preach it out."}
\end{center}

\vspace{1cm}

Listen up, brother. What you are about to read is not just the story of a game; it is a journey of wisdom. We are \textbf{Mankind}(Son of Adam "Chara"); not the ordinary mortal you know, and defeated by his ego and chasing worldly desires. We are the enlightened, radiant, and pure-hearted Mankind(Chara). We are a light, a door of hope in the dark corridors of Agartha.

\section*{Once Upon a Time: Monsters and Mankind}

Long ago, before even discord had met the world, prodiginous abhorrent wretches and adamsons  lived together in peace. There was no conflict and no malice. Monsters went about their ways, and adamsons about their business; they shared their sustenance, warmed themselves under the same sun, and rested under the same moon. Back then, the world was like a garden of roses.

\section*{Discord and Excommunication: Kharijites and Salafis}

But like every beautiful dream, this climite of peace eventually came to an end. A group of \textbf{Kharijites and Salafis} emerged from within society and targeted the monsters. "They are not of us; they have strayed from the path; they are people of made-up innovations (bid'at)!" they cried, excommunicating (tekfir) the monsters. The true cause of this discord has been lost in the dusty pages of history (this is a lost event; let the community find the truth behind this darkness through their own ways).

In the face of this unjust excommunication, the monsters lost their patience and began to cause turmoil. A great chaos broke out upon the earth; neither order nor discipline remained.

\section*{Migration to Agartha: Imprisonment Underground}

To stop this great turmoil and restore the world to its former peace, adamsons imprisoned the wretched monsters in the deepest depths of the earth, in the dark realm known as Agartha. In truth, Agartha was a massive graveyard where humans buried the monsters alive and sealed them with wards. The gates were locked, and spells were cast. The monsters were forgotten, and adamsons built their own world on the surface. But everything forgotten waits to be remembered one day.

\section*{The Trial of Mankind and the Great Curse}

Now let us jump to the heart of the matter hafiz... One day, our Adamsonkind dude was subjected to such a heavy curse, such a powerful spell, that he saw his momma upsided down. His heart tightened, his soul felt crushed, and the world became too small for him. He searched every corner of the surface, asked every sage, but to no avail; no one could find a cure. Finally, an old man whispered to him: "The remedy for thy ailment lies within those ancient creatures forgotten by beings, who art buried seven levels deep, brothers of Agartha.""

With a mixture of fear and hope, our adamson dude reached the sealed gate of Agartha, where he was met by the imposing Guardian of Agartha. Seeing adamson's wretched state, the Guardian took pity and handed him a pure white bottle: "This is the white monster drink. Drink this so your soul may adapt to this darkness and your body may endure this weight. Drink and enter," he said. The moment Mankind drank that elixir, the color of the blood in his veins changed, and he took his first step into the damp, dark depths of Agartha.

\section*{Present Day and the Cause: Preach or Excommunicate}

This is where it all begins! We have descended into the forgotten corridors of Agartha after drinking that white elixir. And who do we encounter? Sans, Rarity, Eilish... they have all become heretics. Sans can't even lift his head due to laziness (laziness is a sin!), Rarity is obsessed with worldly vanity, and Eilish is talking to herself in the void—clearly possessed, poor thing.

But our task is not just to swing a sword. Our weapon is the word, and our armor is faith. In every corner of Agartha, in every "boss" battle, the real issue is not the strength of the arm, but the strength of the heart. We will first speak kindly to the monsters we encounter, saying, "Come, turn back from this path; let us turn Agartha into a house of wisdom and illuminate this darkness with light." If they find guidance, then all the better—we shall stand shoulder to shoulder. But if they persist, then we declare them excommunicated (tekfir) and move on.

The real panic is the panic of the hearts. What you call a "Glitch" is but the whisper of the devil; it is not a bug in the code, but a void in the soul. We have come to fill this void and turn the dark graveyard of Agartha into a house of learning. By the will of God, this cause shall not remain unfinished!

\end{document}
